SST_patterns

### 2019-09-16 SST_patterns.Rmd
minor edits

```{r}
# load("Data/site_list_sub.Rdata")
# # xtable(site_list_sub, auto = TRUE)
# west <- site_list_sub
# west$coast <- "west" # Chnages wc to west
# 
# load("Data/africa_coast.RData")
# 
# ## Downloading the bathy data from NOAA
# # Download mid-res bathymetry data
# # sa_lat <- c(-38, -24.5); sa_lon <- c(11.5, 35.5)
# # sa_bathy <- as.xyz(getNOAA.bathy(lon1 = sa_lon[1], lon2 = sa_lon[2], lat1 = sa_lat[1], lat2 = sa_lat[2], resolution = 4))
# # colnames(sa_bathy) <- c("lon", "lat", "depth")
# # sa_bathy <- sa_bathy[sa_bathy$depth <= 0,]
# # save(sa_bathy, file = "Data_P1/bathy/sa_bathy.RData")
# 
# # Loading in the newly downloaded bathymetry data
# load("Data/bathy/sa_bathy.RData")
# 
# # This function takes one site (e.g. one set of lon/lats) and calculates a shore normal transect
# shore.normal.transect <- function(site, width = 2){
#   # Find the site on the coastline and it's nearest neighbour points
#   coords <- data.frame(lon = site$lon, lat = site$lat)
#   coords2 <- knnx.index(africa_coast[,1:2], as.matrix(coords), k = 1)
#   coords3 <- data.frame(site = site$site, africa_coast[c(coords2-width, coords2+width),]) 
#   coords3 <- coords3[2:1,1:3]
#   # Define the shore normal transect bearing
#   heading <- earth.bear(coords3[1,2], coords3[1,3], coords3[2,2], coords3[2,3]) + 90
#   if(heading >= 360){
#     heading <- heading-360
#   } else {
#     heading <- heading
#   }
#   heading2 <- data.frame(site = site$site, lon = site$lon, lat = site$lat, heading)
#   return(heading2)
# }
# 
# # Creating the transects
# site_transects <- data.frame()
# for(i in 1:length(west$site)){
#  site <- west[i,]
#  site_transect <- shore.normal.transect(site, 2)
#  site_transects <- rbind(site_transects, site_transect)
# }
# 
# # Manually correcting Sea Point and Kommetjie
# site_transects$heading[4:5] <- 290 
# # save(site_transects, file = "Data/site_transects.RData")
# load("Data/site_transects.RData")
# 
# # This function takes one site (e.g. one set of lon/lats) and calculates a shore norm./subal transect
# # It then extracts a lat/ lon point every X kilometres until reaching a specified isobath
# 
# transect.pixel <- function(site, distances){
#   # Extract coordinates
#   coords <- data.frame(lon = site$lon, lat = site$lat)
#   # Find lon/ lats every X metres 
#   pixels <- data.frame()
#   # deep <- 999
#   # distance_multiplier <- 1
#   # while(deep > isobath){
#   for(i in 1:length(distances)){
#     coords2 <- as.data.frame(destPoint(p = coords, b = site$heading, d = distances[i]))
#     sitesIdx <- knnx.index(sa_bathy[,1:2], as.matrix(coords2), k = 1)
#     bathy2 <- sa_bathy[sitesIdx,]
#     bathy2 <- bathy2[complete.cases(bathy2$depth),]
#     bathy3 <- data.frame(site = site$site, lon = bathy2$lon, lat = bathy2$lat, 
#                          heading = site$heading, 
#                          distance = distances[i])
#     pixels <- rbind(pixels, bathy3)
#     coords <- coords2
#   }
#   if(nrow(pixels) < 1){
#     pixels <- data.frame(site, depth = NA)
#   }else{
#     pixels <- pixels
#   }+

@@

pixel_match <- pixel_match %>%
  unite(col = combi, lon_sat, lat_sat, sep = "/", remove = F)

@@

match_func <- function(df){
  match <- SACTN_daily_clusters_sub_1  %>% 
  left_join(df, by = c("site", "date")) %>% 
  na.trim()
  return(match)
}

insitu_MUR <- match_func(df = MUR_data)

# OISST_temp <- OISST %>%
#   unite(col = combi, lon, lat, sep = "/", remove = F) %>% 
#   filter(combi %in% pixel_match$combi)

# combined_OISST_match <- CMC %>% 
#   filter(combi %in% pixel_match$combi)

>>>>

```{r}
# load("Data/site_list_sub.Rdata")
# # xtable(site_list_sub, auto = TRUE)
# west <- site_list_sub
# west$coast <- "west" # Chnages wc to west
# 
# load("Data/africa_coast.RData")
# 
# ## Downloading the bathy data from NOAA
# # Download mid-res bathymetry data
# # sa_lat <- c(-38, -24.5); sa_lon <- c(11.5, 35.5)
# # sa_bathy <- as.xyz(getNOAA.bathy(lon1 = sa_lon[1], lon2 = sa_lon[2], lat1 = sa_lat[1], lat2 = sa_lat[2], resolution = 4))
# # colnames(sa_bathy) <- c("lon", "lat", "depth")
# # sa_bathy <- sa_bathy[sa_bathy$depth <= 0,]
# # save(sa_bathy, file = "Data_P1/bathy/sa_bathy.RData")
# 
# # Loading in the newly downloaded bathymetry data               
# load("Data/bathy/sa_bathy.RData")

# # This function takes one site (e.g. one set of lon/lats) and calculates a shore normal transect
# shore.normal.transect <- function(site, width = 2){
#   # Find the site on the coastline and it's nearest neighbour points
#   coords <- data.frame(lon = site$lon, lat = site$lat)
#   coords2 <- knnx.index(africa_coast[,1:2], as.matrix(coords), k = 1)
#   coords3 <- data.frame(site = site$site, africa_coast[c(coords2-width, coords2+width),]) 
#   coords3 <- coords3[2:1,1:3]
#   # Define the shore normal transect bearing
#   heading <- earth.bear(coords3[1,2], coords3[1,3], coords3[2,2], coords3[2,3]) + 90
#   if(heading >= 360){
#     heading <- heading-360
#   } else {
#     heading <- heading
#   }
#   heading2 <- data.frame(site = site$site, lon = site$lon, lat = site$lat, heading)
#   return(heading2)
# }
# 
# # Creating the transects
# site_transects <- data.frame()
# for(i in 1:length(west$site)){
#  site <- west[i,]
#  site_transect <- shore.normal.transect(site, 2)
#  site_transects <- rbind(site_transects, site_transect)
# }
# 
# # Manually correcting Sea Point and Kommetjie
# site_transects$heading[4:5] <- 290 
# # save(site_transects, file = "Data/site_transects.RData")
# load("Data/site_transects.RData")
# 
# # This function takes one site (e.g. one set of lon/lats) and calculates a shore norm./subal transect
# # It then extracts a lat/ lon point every X kilometres until reaching a specified isobath
# 
# transect.pixel <- function(site, distances){
#   # Extract coordinates
#   coords <- data.frame(lon = site$lon, lat = site$lat)
#   # Find lon/ lats every X metres 
#   pixels <- data.frame()
#   # deep <- 999
#   # distance_multiplier <- 1
#   # while(deep > isobath){
#   for(i in 1:length(distances)){
#     coords2 <- as.data.frame(destPoint(p = coords, b = site$heading, d = distances[i]))
#     sitesIdx <- knnx.index(sa_bathy[,1:2], as.matrix(coords2), k = 1)
#     bathy2 <- sa_bathy[sitesIdx,]
#     bathy2 <- bathy2[complete.cases(bathy2$depth),]
#     bathy3 <- data.frame(site = site$site, lon = bathy2$lon, lat = bathy2$lat, 
#                          heading = site$heading, 
#                          distance = distances[i])
#     pixels <- rbind(pixels, bathy3)
#     coords <- coords2
#   }
#   if(nrow(pixels) < 1){
#     pixels <- data.frame(site, depth = NA)
#   }else{
#     pixels <- pixels
#   }+

@@

@@
